---
title: "Airbnb Listings EDA"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Libraries

DataExplorer for EDA helper functions
Amelia for dealing with Missing Values
Hmisc for correlation analysis

```{r}
suppressWarnings(library(DataExplorer))
suppressWarnings(library(Amelia))
suppressWarnings(library(tidyverse))
suppressWarnings(library(Hmisc))
```

## Load Airbnb Listings

Main Airbnb Dataset with all cumulative listings as at Jan 2018

```{r}
listings_filename = 'G:/Team Drives/STDS - Assignment 2 - 3MDL/Dataset/AirBnB/listings.csv'
listings <- read_csv(listings_filename)
```

TODO: Deal with loading issues

## Data Structure

Dimensions: Approx. 33,000 Listings and 96 Features

```{r}
dim(listings)
```

Memory size of dataset, see if we need to work on subset if too large (135 mb)

```{r}
object.size(listings)
```

Features

```{r}
names(listings)
```

Feature structure

```{r}
str(listings)
```

Head

```{r}
head(listings,10)
```

Tail

```{r}
tail(listings,10)
```


## Summary

5 Point summary of each feature

```{r}
summary(listings)
```

We can see a number of missing values on a number of features

## Missing Data

Use Amelia to explore missing values

```{r}
missmap(listings, main="Missing values vs observed")
```

Use DataExplorer instead to explore missing values

```{r}
plot_missing(listings)
```

TODO: Still not good representation image wise
TODO: Is it MCAR / MNAR?


## Feature Distributions

Look at shape of each feature.

This will only look at discrete (and therfore also give indication of potentially categorical data)

```{r}
plot_bar(listings)
```

Continuous Features Distribution (Data Explorer will only plot histogram for continuous features automatically)

```{r}
plot_histogram(listings)
```


## Feature Correlations

Look at correlations between features

```{r}
plot_correlation(listings, use = "pairwise.complete.obs")
```

Hard to visualize due to too many features, instead print the correlated features using the Hmisc package rcorr function.
This also allows p-values associated with the correlation.
Only want list of correlations where 1) 5% significance level and 2) moderate to strong correlation i.e. > 0.4

```{r}

# have also not checked pearson assumptions
options(warn=-1)
correlations <- rcorr(as.matrix(as.data.frame(lapply(listings, as.numeric))), type="pearson")
# Issue with as.matrix due to NA, getting storage error
options(warn=0)

n_col = dim(listings)[2]
for (i in 1:n_col){
  for (j in 1:n_col){
    if ( !is.na(correlations$P[i,j])){
      if ( correlations$P[i,j] < 0.05 && abs(correlations$r[i,j]) > 0.4) {
        print(paste(rownames(correlations$P)[i], "-" , colnames(correlations$P)[j], ": ", correlations$r[i,j]))
      }
    }
  }
}
```


## Feature Outliers

Look at outliers for each features. Note this is univariate analysis.

```{r}
# Takes too long
#plot_boxplot(listings, by="price")

#outlier(listings[!is.na(listings)]$price)

```
